A graph-based data model for interactive evolutionary computation

### 2017-01-19 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
changes

\begin{itemize}
  \item { \tt Individual-Individual} The relationships between individuals in the
  population are naturally expressed as a tree, or a graph when both ancestors 
  and descendants are considered. Other semantic relations can also be of interest
  for instance similarity or composition.

  \item {\tt User-Individual}
  Many kind of relationships between users and individuals,
  can be expressed using common actions found in social networks;
  for instance: share, like, rate or add to collection [cite Activity Streams 2.0
  syntax (https://www.w3.org/TR/activitystreams-vocabulary)]. In IEAs these
  relationships are used to assign a single or a collection of
  fitness values to individuals [cite ES-I].

  \item {\tt User-User}
  Relationship between users can also be modeled 
  as a social network, with well stablished semantics, algorithms and metrics (cite).
  A graph model could eneable researchers to find other ways of identifyng leaders of 
  opinion or measuring the similarity between user\'s preferences. 
  These measures can then be used by recommender algorithms selecting 
  individuals according users\' preferences.

@@

\section{EvoSpace-Interactive}
\label{sec:evospace-i} 
As a case study, a IEA was implented using the 
EvoSpace-Interactive (ES-I) platform \cite{garcia2013evospace}. %citation
A brief description of the aplication is presented next, focusing
on the data elements that where ported to the graph model.

\subsection{Fitness Assignment}
\label{sec:col}
The ES-I platform employs a collaborative technique,
where several registered users assign a quality assessment to a single
individual and then an aggregated fitness value is calculated. The fitness
assigned to each individual depends on the taste of each particular user, 
resulting in a many-to-many relationship between users and individuals. 
Many systems query this user-individual relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular individual, or the the user with more participation \cite{picbreeder}.
In order to do this, data about individuals %what? Maybe data
                                %about individuals? - JJ
must be permanently stored, even
if they are no longer in the active population.

\subsection{Collaboration}
\label{sec:col}
After entering the web application by using their Facebook account,
users can collaborate with their Facebook friends, 
sharing those individuals they like, or by taking individuals
from their friend\'s collections by using the web interface depicted 
in Figure \ref{fig:web}

@@

\begin{figure*}
  \captionsetup{justification=centering,margin=2cm}
  \centering
  \setlength\fboxsep{0pt}
  \setlength\fboxrule{0.7pt}
  \fbox{\includegraphics[width=10cm,height=10cm,keepaspectratio]{img/framework.png}}
  \caption{User-Centerd Framework.}
  \label{fig:uc_framework}       
\end{figure*}

@@

\begin{itemize}
  \item { \tt Interactive Evolutionary Computational system.}  
  This is the real world system that we are going to represent in the model, 
  it consist of human users and their interactions with one or more individuals from
  the population. There are many ways in which humans could interact 
  with indivuals, this could be through a mobile device, a user interface 
  or by interacting with real world objects generated as part of the algorithm 
  [cite evodraw o unplugged].
  There is also the posibility that fitness or even part of the search 
  to be done by devices lended by the human [cite nodio].
  The information gathered through the interaction is the primary concern
  as it will guide the search.

  \item {\tt IEC Data Model}
  A data model is used to describe the IEC system prior to a physical 
  implementation. 
  %% This block is maybe not needed but in our ES-I implementation
  %% we use Relational (PosgreSQL), Objects (JSON-Redis) and Graphs (Neo4J)
  Depending on the domain several techniques can be used.
  Parts of the system could be better described by an Entity relationship 
  modeling to be used in a relational database or a Class Digram for a 
  key-value store. 
  %%
  %%
  A graph is proposed for modelling the social network
  of users and their interaction with the population. This database 
  is the back-end of the system, is used by the EA and the user interface.

  \item {\tt Evolutionary Algorithm} 
  The EA algorithm queries the graph model, and then updates those nodes that 
  are part of the population. The EA could also be done with the help of
  humans, for instance in the XY project [cite] artists physicaly created
  the new population.  
\end{itemize}

@@

\subsection{IEC Graph Conceptual Model}

In this section the Graph Model is presented,

\subsection{Experiments}
\label{sec:experiments}

\subsection{Conclusions}
\label{sec:conclusions}

>>>>

\begin{itemize}
  \item Individual-Individual. The relationships between individuals in the
  population are naturally expressed as a tree, or a graph when both ancestors 
  and descendants are considered. Other semantic relations can also be of interest
  for instance similarity or composition.

  \item User-Individual.
  Many kind of relationships between users and individuals,
  can be expressed using common actions found in social networks;
  for instance: share, like, rate or add to collection [cite Activity Streams 2.0
  syntax (https://www.w3.org/TR/activitystreams-vocabulary)]. In IEAs these
  relationships are used to assign a single or a collection of
  fitness values to individuals [cite ES-I].

  \item User-User.
  Relationship between users can also be modeled 
  as a social network, with well stablished semantics, algorithms and metrics (cite).
  A graph model could eneable researchers to find other ways of identifyng leaders of 
  opinion or measuring the similarity between user\'s preferences. 
  These measures can then be used by recommender algorithms selecting 
  individuals according users\' preferences.

@@

\subsection{EvoSpace-Interactive}
\label{sec:evospace-i} 
As a case study, a IEA was implented using the 
EvoSpace-Interactive (ES-I) platform \cite{garcia2013evospace}. %citation
A brief description of the aplication is presented next, focusing
on the data elements that where ported to the graph model.

\subsubsection{Fitness Assignment}
\label{sec:col}
The ES-I platform employs a collaborative technique,
where several registered users assign a quality assessment to a single
individual and then an aggregated fitness value is calculated. The fitness
assigned to each individual depends on the taste of each particular user, 
resulting in a many-to-many relationship between users and individuals. 
Many systems query this user-individual relation to extract relevant
knowledge about the process and the population, for instance showing the
most popular individual, or the the user with more participation \cite{picbreeder}.
In order to do this, data about individuals %what? Maybe data
                                %about individuals? - JJ
must be permanently stored, even
if they are no longer in the active population.

\subsubsection{Collaboration}
\label{sec:col}
After entering the web application by using their Facebook account,
users can collaborate with their Facebook friends, 
sharing those individuals they like, or by taking individuals
from their friend\'s collections by using the web interface depicted 
in Figure \ref{fig:web}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth,height=8cm,keepaspectratio]{img/framework.png}

  \caption{Human-Centerd Framework.}
  \label{fig:uc_framework}       
\end{figure}

@@

\begin{itemize}
  \item Interactive Evolutionary Computational system. 
  This is the real world system that we are going to represent in the model, 
  it consist of human users and their interactions with one or more individuals from
  the population. There are many ways in which humans could interact 
  with indivuals, this could be through a mobile device, a user interface 
  or by interacting with real world objects generated as part of the algorithm 
  [cite evodraw o unplugged].
  There is also the posibility that fitness or even part of the search 
  to be done by devices lended by the human [cite nodio].
  The information gathered through the interaction is the primary concern
  as it will guide the search.

  \item IEC Data Model.
  A data model is used to describe the IEC system prior to a physical 
  implementation. 
  %% This block is maybe not needed but in our ES-I implementation
  %% we use Relational (PosgreSQL), Objects (JSON-Redis) and Graphs (Neo4J)
  Depending on the domain several techniques can be used.
  Parts of the system could be better described by an Entity relationship 
  modeling to be used in a relational database or a Class Digram for a 
  key-value store. 
  %%
  %%
  A graph is proposed for modelling the social network
  of users and their interaction with the population. This database 
  is the back-end of the system, is used by the EA and the user interface.

  \item Evolutionary Algorithm. 
  The EA algorithm queries the graph model, and then updates those nodes that 
  are part of the population. The EA could also be done with the help of
  humans, for instance in the XY project [cite] artists physicaly created
  the new population.  
\end{itemize}

@@

\section{IEC Graph Conceptual Model}

A graph is composed of two fundamental entities: nodes and relationships,
both having attributes. Nodes are abstractions of the objects in the real 
world system, and relationships describe their interactions. Types describe
the attributes describing an entity, First we describe the types of nodes and  relationships in the system.

\subsection{Node Types}
\begin{itemize}

\item Users. This nodes represent the human users of the system and have 
the attributes: {\tt id} a unique identifier, {\tt name}  and {\tt created}
specifing the  creation date (time stamp) of the node.

\item Individual. This type of node has the following attributes: 
{\tt id}, {\tt chromosome}  and {\tt views} this is 
the amount that users have seen or interacted with this individual and
 {\tt created}.
\item Collection. This type of nodes represent the collections belonging
to users, their attributes are {\tt id}, 
{\tt name}, {\tt created} and {\tt is_private} indicating if this collection
contents are shared with others. 
\end{itemize}

\subsection{Relationships Type}
%%
%% Explain relations

The {\tt likes} relation describes the interaction between a User and
an Individual in which a rating value is assigned. In the current application
a user is allowed to rate an Individual multiple times, so the date of the 
interactions is also of interest.

\begin{itemize} 
\item id. 
\item created. 
\item rate.
\end{itemize}

The relation {\tt knows} connects two users that know each other. This relation
is "unique" meaning that it can not be repeted between a pair of nodes.

The relation {\tt parent} describes what Individual is the parent of a new
Individual and is also unique.

The relation {\tt has} describes an ownership relation between users and
those collections they own. Also a collection {\tt has}  individuals stored
in them.

In figure \ref{fig:Has_edge} the edge {\tt has} attributes and the relationship between certain nodes $user$, $individual$ and $collection$ are shown.

\begin{figure*}
\captionsetup{justification=centering,margin=2cm}
\centering
\setlength\fboxsep{0pt}
\setlength\fboxrule{0.7pt}
\fbox{\includegraphics[width=5cm,height=5cm,keepaspectratio]{img/edge_properties_has.png}}
\caption{HAS edge Properties.}
\label{fig:Has_edge}       
\end{figure*}

\section{Case Study}
\label{sec:experiments}

\section{Conclusion}
\label{sec:conclusions}
